%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% Letter paper size by default, use ''a4paper" for A4
\documentclass[11pt, letterpaper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-darknight}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
% \photo[rectangle,edge,right]{./examples/profile}
\name{Dylan}{Rumbold}
\position{Network Engineer{\enskip\cdotp\enskip}Security Tester{\enskip\cdotp\enskip}Software Developer}
\address{1739 Leah Drive, North Tonawanda, New York 14120}

\mobile{(+1) 716-245-3101}
\email{dylan.rumbold@gmail.com}
%\homepage{www.posquit0.com}
\github{drumbold}
\linkedin{drrumbold}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \extrainfo{extra informations}

%\quote{``Be the change that you want to see in the world."}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {Talent Attraction at Indeed}
  {}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Job Application for IT/Linux Systems Administrator}
% How the letter is opened
\letteropening{Dear Mrs. Guerrero,}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
\letterenclosure[Attached]{Résumé}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[R]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}%
  {Dylan Rumbold{\enskip\cdotp\enskip}Cover Letter}
  {}

% Print the title with above letter informations
\makelettertitle
  {}

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

%\lettersection{About Me}
I hope this letter finds you well. My name is Dylan, and I'm a programmer at National Fuel. Recently, I began searching for a new challenge, something more interesting than my current position and that is when I came across your posting for an IT/Linux Systems Administrator - Ref\# D1343. With my background in computer science and my experience, especially with OS X, I would make a great addition to the team.

I bought my first mac my freshman year of high school. After putting away money for years in anticipation of a big purchase and watching my Mom's old Dell die in my lap I knew what I was going to buy. From that point on I have completely engrossed myself in the Apple ecosystem learning all about OS X, the included apps and filesystem, its UNIX base and familiarizing myself with bash. Years of experience with macs and always trying to get the most out of my personal computer have given me knowledge rivaling that of an Apple Store Genius. 

In addition, I have experience with networking and programming through my formal education and early career opportunities. Classes including networking and network security helped prepare me for my first job while in college setting up workstations,  wiring network closets, running cables through the datacenter and installing hundreds of 1Gb NICs. I also began working with Python creating small CLI programs and setting up flask servers. 

 The exploding job market and reputation around being a developer led me to my current position as a programmer. My time at National Fuel has taught me a lot about all aspects of the software development life cycle, but has not intrigued me the way positions on the operations side of technology have.

I look forward to discussing the position further and learning more about the opportunities available at Indeed. If I can provide anything else you might need please let me know. I look forward to hearing from you. I can be reached at dylan.rumbold@gmail.com and 716-245-3101.

Thank you for your consideration.

%\lettersection{Why Google?}
%Suspendisse commodo, massa eu congue tincidunt, elit mauris pellentesque orci, cursus tempor odio nisl euismod augue. 

%\lettersection{Why Me?}
%Duis sit amet magna ante, at sodales diam. Aenean consectetur porta risus et sagittis. 

\end{cvletter}


%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter informations
\makeletterclosing

\end{document}
