%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% Letter paper size by default, use ''a4paper" for A4
\documentclass[11pt, letterpaper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-darknight}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
% \photo[rectangle,edge,right]{./examples/profile}
\name{Dylan}{Rumbold}
\position{Network Engineer{\enskip\cdotp\enskip}Security Tester{\enskip\cdotp\enskip}Software Developer}
\address{1739 Leah Drive, North Tonawanda, New York 14120}

\mobile{(+1) 716-245-3101}
\email{dylan.rumbold@gmail.com}
%\homepage{www.posquit0.com}
\github{drumbold}
\linkedin{drrumbold}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \extrainfo{extra informations}

%\quote{``Be the change that you want to see in the world."}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {M\&T Bank Talent Acquisition}
  {}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Job Application for CyberSecurity Vulnerability Risk Analyst}
% How the letter is opened
\letteropening{Dear Mrs. Skowronski,}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
\letterenclosure[Attached]{Résumé}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[R]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}%
  {Dylan Rumbold{\enskip\cdotp\enskip}Cover Letter}
  {}

% Print the title with above letter informations
\makelettertitle
  {}

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

%\lettersection{About Me}
I hope this letter finds you well. My name is Dylan, and I'm a programmer at National Fuel. Recently, I began searching for a new challenge, something more interesting than my current position and that is when I came across your posting for a cybersecurity vulnerability risk analyst - 3D9LK. With my background in computer science and my ingenuity when problem solving, I would be a great addition to the team.

Throughout my college and professional career cybersecurity has always been very interesting to me. I really enjoy trying to get around restrictions and outsmart defenses which is why I feel very passionate about this positions like this. While pursuing my computer and information science degree, I received a minor in computer crime after taking many computer forensics and ethical hacking courses. Those were some of the most interesting classes I took and the skills I learned during those classes have set me up for a position like this one. Having experience analyzing hard drive images using FTK and even receiving my AccessData Certified Examiner certificate give me the opportunity to start contributing on day one. I also had the chance to begin preparing for certified ethical hacker exam. In addition to reading and studying, our labs were set up in order for us to gain some real world experience. My included résumé will reveal my prior work experience, detailing some of my history in information security. The exploding job market and reputation around being a developer led me to my current position as a programmer. My time at National Fuel has taught me a lot about all aspects of the software development life cycle, but has not intrigued me the way information security positions have.

I look forward to discussing the position further and learning more about the opportunities available at M\&T. If I can provide anything else you might need please let me know. I look forward to hearing from you. I can be reached at dylan.rumbold@gmail.com and 716-245-3101.

Thank you for your consideration.

%\lettersection{Why Google?}
%Suspendisse commodo, massa eu congue tincidunt, elit mauris pellentesque orci, cursus tempor odio nisl euismod augue. 

%\lettersection{Why Me?}
%Duis sit amet magna ante, at sodales diam. Aenean consectetur porta risus et sagittis. 

\end{cvletter}


%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter informations
\makeletterclosing

\end{document}
